### 2017-06-29 paper.tex

Lessons do not maintain themselves.
For technical lessons, software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case, what was cutting edge in 2017 may be dated
and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

The focus accordingly needs to be on creating a community.
Authors cannot be expected to maintain continual vigilance on a lesson,
but this is necessary if one expects continual use of a lesson!
By working online, creating opportunities for collaboration
and contribution, many eyes can keep the lesson usable.
As we describe in Rule~5,
this only works if you make space for
little contributions just as you do for larger ones.

@@

@@

If lessons are being released regularly,
automate the process,
and archive old versions of lessons in a discoverable location for reference.
Also make sure that everyone involved knows what ``done'' look like,
i.e.,
which outstanding issues have to be addressed
and how it has to be formatted
in order for the next release to go out.
A simple checklist stored with the lesson materials is good enough to start,
but as time goes by,
the community may want to use an issue tracking system of some sort
so that work items can be assigned to specific people
and then ticked off as they are completed.

>>>>

@@

Encouraging and enabling individual contributions is necessary but not sufficient.
For technical lessons,
software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case,
what was cutting edge in 2017 may be dated and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

The focus accordingly needs to be on creating a community in which contributors support each other
rather than relying on a small group of stewards.
Authors cannot be expected to maintain continual vigilance on a lesson,
but this is necessary if one expects continual use of a lesson.
By working online, creating opportunities for collaboration
and contribution, many eyes can keep the lesson usable.
As we describe in Rule~5,
this only works if you make space for
little contributions just as you do for larger ones.

@@

If lessons are being released regularly,
automate the process.
Old versions of lessons should be archived in a discoverable location for reference.
